Bosnia: Voting behavior of MPs in the House of Representatives

### 2021-02-14 _post/2020-02-07-bih-voting-behavior-of-mps-in-house-of-representatives/bih-voting-behavior-of-mps-in-house-of-representatives.Rmd
main update

bgr_color<- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=background-color:).*?(?=;)")) %>% str_trim()

blog_theme <- function(){
    hrbrthemes::theme_ipsum_rc() +
    theme(
        axis.text.x = element_text(angle=0, size=10),
        axis.title = element_blank(),
        legend.position = "bottom",
        legend.justification = "left",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(size = 18, 
                                  face="bold", 
                                  margin=margin(b=0.3, unit="cm")),
        plot.title.position="plot",
        plot.background= element_rect(fill=bgr_color, color=bgr_color),
        plot.subtitle = element_text(size = 15, color = "grey30"),
        plot.margin=margin(l=0, t=0.5, b=0.5, unit="cm"),
       # plot.caption = element_text(hjust=c(0,1)),
        panel.spacing.x = unit(0, "cm"))}

@@

                  theme = theme_ipsum_rc()) &
  theme(legend.position = "bottom",
        plot.background=element_rect(fill=bgr_color, color=bgr_color),
        plot.margin=margin(b=0, t=0, l=0, r=0, unit="cm"),
        legend.text = element_text(size=12),
        legend.justification = "left") 
```

@@

plot_df_outcome_chambers_combined <- df_outcome_chambers_combined  %>% 
  ggplot()+
  labs(title="Outcome of bills by house",
       x="final status in House of Representatives",
       y=str_wrap("final status in House of Peoples", 20),
       caption=my_caption)+
  geom_tile(aes(x=as.numeric(HoR_outcome_label),
                y=as.numeric(HoP_outcome_label),
                fill=n_obs))+
  geom_text(data=. %>% filter(n_obs!=0),
              aes(x=as.numeric(HoR_outcome_label),
                y=as.numeric(HoP_outcome_label),
                label=paste0(n_obs, " (",
                             percent(n_rel, accuracy = 0.1),
                             ")")),
            family = "Roboto Condensed",
            color = "grey30",
            hjust = .5,
            # group = name,
            stat="identity")+
  scale_fill_gradient(low="white", high="steelblue",
                      na.value="white")+
  scale_x_continuous(labels=levels(df_outcome_chambers_combined$HoR_outcome_label) %>% map_chr(., label_wrap(15)),
                     breaks=seq(1, length(unique(df_outcome_chambers_combined$HoR_outcome_label))),
                     sec.axis = dup_axis())+
  scale_y_continuous(labels=levels(df_outcome_chambers_combined$HoP_outcome_label) %>% map_chr(., label_wrap(20)),
                     breaks=seq(1, length(unique(df_outcome_chambers_combined$HoP_outcome_label))),
                     sec.axis = dup_axis(),
                     trans="reverse")+
  blog_theme()+
  theme(axis.text.x.top=element_blank(),
        axis.title.x.top = element_text(hjust=0, size=11),
        axis.title.x.bottom = element_blank(),
        axis.text.y.left=element_blank(),
        axis.title.y.left = element_text(hjust=0, size=11),
        axis.title.y.right = element_blank(),
        #axis.text.x.bottom=element_text(angle=0, hjust=.5),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        panel.border = element_rect(color="grey30", fill=NA),
        axis.title.y = element_text(angle=0),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position = "plot",
        plot.background= element_rect(fill=bgr_color, color=bgr_color),
        plot.margin=margin(l=0, r=0, b=0, unit="cm"),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.caption.position = "plot",
        plot.caption = element_text(color = "grey30", hjust = c(0, 1)))

@@

plots_tile <- plots_tile %>% 
  ggplot()+
  labs(x="items voted at",
       y="Member of House of Representative",
       subtitle="451 decisions in total; 2014-2018 legislative period.",
       title="House of Representative: Vote choice by individual MPs per decision",
       caption=my_caption)+
  geom_tile(aes(x=reorder(record_id, session_date),
                y=fct_rev(delegate_name_family),
                fill=vote))+
  # scale_y_discrete(label=delegate_name_2)+
  scale_fill_manual(values=voting_colors,
                    na.value="white")+
  theme_ipsum_rc() +
  theme(axis.text.x=element_blank(),
        axis.title.x=element_text(hjust=0),
        strip.text = element_text(face="bold"),
        panel.background = element_rect(fill=bgr_color, color=bgr_color),
        panel.grid.major = element_blank(),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.margin=margin(l=0, t=0.5, b=0.5, unit="cm"),
        plot.title.position = "plot",
        plot.caption = element_text(hjust=c(0, 1)),
        plot.background= element_rect(fill=bgr_color, color=bgr_color),
        legend.position = "top",
        legend.justification = "left")+
  facet_wrap(vars(party),
             ncol = 3,
             scales="free_y")

@@

df_votes_delegates %>% 
  mutate(delegate_name_3=str_extract(delegate_name_2, "[:alpha:]+,\\s[:alpha:]?")) %>% 
  ggplot()+
  labs(title="HoR members' voting decision by category during 2014-2018 legislative period (in %)",
       subtitle ="In how many % of all her votes did the MP vote/was.... Absolute number in category and total in brackets.",
       caption=my_caption)+
  geom_bar(aes(x=reorder_within(paste0(delegate_name_3, " (", party, ")"), n_votes_cat_rel, vote),
               y=n_votes_cat_rel,
               fill=entity),
           stat="identity",
           position=position_stack())+
  geom_text(aes(x=reorder_within(paste0(delegate_name_3, " (", party, ")"), n_votes_cat_rel, vote),
                y=1.2,
                label=paste0(scales::percent(n_votes_cat_rel, accuracy =0.1), " (", n_votes_cat, "/", n_votes_total, ")")),
            family = "Roboto Condensed",
            color = "grey30",
            hjust = 1,
            stat="identity")+
  scale_fill_paletteer_d("ggsci::default_jama")+
  scale_x_reordered()+
  scale_y_continuous(minor_breaks = NULL,
                     labels=scales::label_percent(accuracy=1),
                     breaks=seq(0,0.8,.1),
                     expand=expansion(mult=c(0, 0)))+
  theme_ipsum_rc()+
  theme(axis.text.x = element_text(angle=90),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.spacing = unit(0, "cm"),
        strip.text = element_text(face="bold"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust=c(0,1)),
        plot.margin=margin(l=0, t=0.5, b=0.5, r=0, unit="cm"),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.background=element_rect(fill=bgr_color, color=bgr_color),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.justification = "left")+
  lemon::facet_rep_wrap(~vote,
                        repeat.tick.labels = T,
                        ncol=2,
                        scales="free_y")+
  coord_flip()

@@

df_party_voting %>% 
  ggplot()+
  geom_bar(aes(x=tidytext::reorder_within(party, n_rel, within=vote),
               fill=vote,
               y=n_rel),
           stat="identity")+
  geom_text(aes(x=tidytext::reorder_within(party, n_rel, within=vote),
                #y=n_rel+.1,
                y=1.1,
                label=paste0(n_obs, "/", n_total, 
                             " (", 
                             scales::percent(n_rel, accuracy=.1),
                             ")")),
            hjust=1,
            size=4,
            family = "Roboto Condensed",
            color = "grey30",
            stat="identity")+
  scale_x_reordered()+
  facet_rep_wrap(vars(vote),
                 repeat.tick.labels = T,
                 ncol=2,
             scales="free_y")+
  scale_y_continuous(expand=expansion(mult=0),
                     limits=c(0, 1.2),
                     labels=scales::label_percent(accuracy=1),
                     breaks=seq(0, .7, .25))+
  scale_fill_manual(values=voting_colors)+
  coord_flip()+
  theme_ipsum_rc()+
  theme(plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position="plot",
        plot.margin=margin(l=0, t=0.5, b=0.5, r=0, unit="cm"),
        plot.background=element_rect(fill=bgr_color, color=bgr_color),
        panel.grid.major.y =  element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none",
        strip.text = element_text(face="bold"),
        axis.title.y=element_blank(),
        axis.title.x=element_text(hjust=0),
        plot.caption = element_text(hjust=c(0,1)))+
  labs(title="Parties' voting decisions per category (HoR)",
       subtitle="% of all decisions by members of each party; Legislative period 2014-2018.",
       caption=my_caption,
       y="voting decisions in category as % of all decisions by all MPs of each party")

@@

plot_delegates <- df_delegate_voting %>% 
  group_split(vote) %>% 
  map(~ggplot(., aes(x=reorder_within(party, desc(perc), ethnicity),
                     y=perc,
                     group=party,
                     tooltip=paste0(delegate_name, "\n",
                                   nobs, " out of ",
                                   total.votes, "\n",
                                   "ratio:", 
                                   scales::percent(perc)),
                     #tooltip=delegate_name,
                     color=ethnicity))+
        geom_jitter_interactive(width=0.03)+
        geom_boxplot(aes(weight=nobs))+
        labs(title=paste(unique(.$vote)))+
        hrbrthemes::theme_ipsum_rc()+
        theme(legend.position="none",
              plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
              plot.subtitle = element_text(size = 12, color = "grey30"),
              axis.title = element_blank(),
              axis.text.x=element_text(angle=45,
                                       vjust=1,
                                       hjust=1,
                                       size=11),
              strip.text.y = element_text(angle=180, 
                                          vjust=1,
                                          hjust=1),
              plot.margin = margin(t=0, b=0, unit="cm"),
              panel.grid.minor = element_blank(),
              panel.grid.major.x = element_blank(),
              panel.spacing.x = unit(0.3, "cm"),
              plot.background=element_rect(fill=bgr_color, color=bgr_color),
              panel.spacing.y = unit(0.3, "cm"))+
        scale_y_continuous(labels=scales::label_percent(accuracy=1),
                           minor_breaks = NULL,
                           limits=c(0,NA),
                           position = "right",
                           sec.axis = dup_axis())+
        scale_x_reordered()+
        scale_color_manual(values=colors_ethnicity, na.value="grey")+
        #scale_color_paletteer_d("ggsci::default_jama")+
        facet_row(~ethnicity,
                  # switch = "y",
                  scales="free_x",
                  space="free"))

>>>>

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=blog-bg-color:).*?(?=;)")) %>%
  str_trim() %>% 
  str_extract(., regex("^#\\S+"))

blog_theme <- function(){
    hrbrthemes::theme_ipsum_rc() +
    theme(
        axis.text.x = element_text(angle=0, size=10),
        axis.title = element_blank(),
        legend.position = "bottom",
        legend.justification = "left",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(size = 18, 
                                  face="bold", 
                                  margin=margin(b=0.3, unit="cm")),
        plot.title.position="plot",
        plot.background= element_rect(fill=plot_bg_color, color=plot_bg_color),
        plot.subtitle = element_text(size = 15, color = "grey30"),
        plot.margin=margin(l=0, t=0.5, b=0.5, unit="cm"),
       # plot.caption = element_text(hjust=c(0,1)),
        panel.spacing.x = unit(0, "cm"))}

@@

                  theme = theme_ipsum_rc()) &
  theme(legend.position = "bottom",
        plot.background=element_rect(fill=plot_bg_color, color=plot_bg_color),
        plot.margin=margin(b=0, t=0, l=0, r=0, unit="cm"),
        legend.text = element_text(size=12),
        legend.justification = "left") 
```

@@

plot_df_outcome_chambers_combined <- df_outcome_chambers_combined  %>% 
  ggplot()+
  labs(title="Outcome of bills by house",
       x="final status in House of Representatives",
       y=str_wrap("final status in House of Peoples", 20),
       caption=my_caption)+
  geom_tile(aes(x=as.numeric(HoR_outcome_label),
                y=as.numeric(HoP_outcome_label),
                fill=n_obs))+
  geom_text(data=. %>% filter(n_obs!=0),
              aes(x=as.numeric(HoR_outcome_label),
                y=as.numeric(HoP_outcome_label),
                label=paste0(n_obs, " (",
                             percent(n_rel, accuracy = 0.1),
                             ")")),
            family = "Roboto Condensed",
            color = "grey30",
            hjust = .5,
            # group = name,
            stat="identity")+
  scale_fill_gradient(low="white", high="steelblue",
                      na.value="white")+
  scale_x_continuous(labels=levels(df_outcome_chambers_combined$HoR_outcome_label) %>% map_chr(., label_wrap(15)),
                     breaks=seq(1, length(unique(df_outcome_chambers_combined$HoR_outcome_label))),
                     sec.axis = dup_axis())+
  scale_y_continuous(labels=levels(df_outcome_chambers_combined$HoP_outcome_label) %>% map_chr(., label_wrap(20)),
                     breaks=seq(1, length(unique(df_outcome_chambers_combined$HoP_outcome_label))),
                     sec.axis = dup_axis(),
                     trans="reverse")+
  blog_theme()+
  theme(axis.text.x.top=element_blank(),
        axis.title.x.top = element_text(hjust=0, size=11),
        axis.title.x.bottom = element_blank(),
        axis.text.y.left=element_blank(),
        axis.title.y.left = element_text(hjust=0, size=11),
        axis.title.y.right = element_blank(),
        #axis.text.x.bottom=element_text(angle=0, hjust=.5),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        panel.border = element_rect(color="grey30", fill=NA),
        axis.title.y = element_text(angle=0),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position = "plot",
        plot.background= element_rect(fill=plot_bg_color, color=plot_bg_color),
        plot.margin=margin(l=0, r=0, b=0, unit="cm"),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.caption.position = "plot",
        plot.caption = element_text(color = "grey30", hjust = c(0, 1)))

@@

plots_tile <- plots_tile %>% 
  ggplot()+
  labs(x="items voted at",
       y="Member of House of Representative",
       subtitle="451 decisions in total; 2014-2018 legislative period.",
       title="House of Representative: Vote choice by individual MPs per decision",
       caption=my_caption)+
  geom_tile(aes(x=reorder(record_id, session_date),
                y=fct_rev(delegate_name_family),
                fill=vote))+
  # scale_y_discrete(label=delegate_name_2)+
  scale_fill_manual(values=voting_colors,
                    na.value="white")+
  theme_ipsum_rc() +
  theme(axis.text.x=element_blank(),
        axis.title.x=element_text(hjust=0),
        strip.text = element_text(face="bold"),
        panel.background = element_rect(fill=plot_bg_color, color=plot_bg_color),
        panel.grid.major = element_blank(),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.margin=margin(l=0, t=0.5, b=0.5, unit="cm"),
        plot.title.position = "plot",
        plot.caption = element_text(hjust=c(0, 1)),
        plot.background= element_rect(fill=plot_bg_color, color=plot_bg_color),
        legend.position = "top",
        legend.justification = "left")+
  facet_wrap(vars(party),
             ncol = 3,
             scales="free_y")

@@

df_votes_delegates %>% 
  mutate(delegate_name_3=str_extract(delegate_name_2, "[:alpha:]+,\\s[:alpha:]?")) %>% 
  ggplot()+
  labs(title="HoR members' voting decision by category during 2014-2018 legislative period (in %)",
       subtitle ="In how many % of all her votes did the MP vote/was.... Absolute number in category and total in brackets.",
       caption=my_caption)+
  geom_bar(aes(x=reorder_within(paste0(delegate_name_3, " (", party, ")"), n_votes_cat_rel, vote),
               y=n_votes_cat_rel,
               fill=entity),
           stat="identity",
           position=position_stack())+
  geom_text(aes(x=reorder_within(paste0(delegate_name_3, " (", party, ")"), n_votes_cat_rel, vote),
                y=1.2,
                label=paste0(scales::percent(n_votes_cat_rel, accuracy =0.1), " (", n_votes_cat, "/", n_votes_total, ")")),
            family = "Roboto Condensed",
            color = "grey30",
            hjust = 1,
            stat="identity")+
  scale_fill_paletteer_d("ggsci::default_jama")+
  scale_x_reordered()+
  scale_y_continuous(minor_breaks = NULL,
                     labels=scales::label_percent(accuracy=1),
                     breaks=seq(0,0.8,.1),
                     expand=expansion(mult=c(0, 0)))+
  theme_ipsum_rc()+
  theme(axis.text.x = element_text(angle=90),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.spacing = unit(0, "cm"),
        strip.text = element_text(face="bold"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position = "plot",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust=c(0,1)),
        plot.margin=margin(l=0, t=0.5, b=0.5, r=0, unit="cm"),
        plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.background=element_rect(fill=plot_bg_color, color=plot_bg_color),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.justification = "left")+
  lemon::facet_rep_wrap(~vote,
                        repeat.tick.labels = T,
                        ncol=2,
                        scales="free_y")+
  coord_flip()

@@

df_party_voting %>% 
  ggplot()+
  geom_bar(aes(x=tidytext::reorder_within(party, n_rel, within=vote),
               fill=vote,
               y=n_rel),
           stat="identity")+
  geom_text(aes(x=tidytext::reorder_within(party, n_rel, within=vote),
                #y=n_rel+.1,
                y=1.1,
                label=paste0(n_obs, "/", n_total, 
                             " (", 
                             scales::percent(n_rel, accuracy=.1),
                             ")")),
            hjust=1,
            size=4,
            family = "Roboto Condensed",
            color = "grey30",
            stat="identity")+
  scale_x_reordered()+
  facet_rep_wrap(vars(vote),
                 repeat.tick.labels = T,
                 ncol=2,
             scales="free_y")+
  scale_y_continuous(expand=expansion(mult=0),
                     limits=c(0, 1.2),
                     labels=scales::label_percent(accuracy=1),
                     breaks=seq(0, .7, .25))+
  scale_fill_manual(values=voting_colors)+
  coord_flip()+
  theme_ipsum_rc()+
  theme(plot.subtitle = element_text(size = 12, color = "grey30"),
        plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
        plot.title.position="plot",
        plot.margin=margin(l=0, t=0.5, b=0.5, r=0, unit="cm"),
        plot.background=element_rect(fill=plot_bg_color, color=plot_bg_color),
        panel.grid.major.y =  element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none",
        strip.text = element_text(face="bold"),
        axis.title.y=element_blank(),
        axis.title.x=element_text(hjust=0),
        plot.caption = element_text(hjust=c(0,1)))+
  labs(title="Parties' voting decisions per category (HoR)",
       subtitle="% of all decisions by members of each party; Legislative period 2014-2018.",
       caption=my_caption,
       y="voting decisions in category as % of all decisions by all MPs of each party")

@@

plot_delegates <- df_delegate_voting %>% 
  group_split(vote) %>% 
  map(~ggplot(., aes(x=reorder_within(party, desc(perc), ethnicity),
                     y=perc,
                     group=party,
                     tooltip=paste0(delegate_name, "\n",
                                   nobs, " out of ",
                                   total.votes, "\n",
                                   "ratio:", 
                                   scales::percent(perc)),
                     #tooltip=delegate_name,
                     color=ethnicity))+
        geom_jitter_interactive(width=0.03)+
        geom_boxplot(aes(weight=nobs))+
        labs(title=paste(unique(.$vote)))+
        hrbrthemes::theme_ipsum_rc()+
        theme(legend.position="none",
              plot.title = element_text(size = 14, face="bold", margin=margin(b=0.3, unit="cm")),
              plot.subtitle = element_text(size = 12, color = "grey30"),
              axis.title = element_blank(),
              axis.text.x=element_text(angle=45,
                                       vjust=1,
                                       hjust=1,
                                       size=11),
              strip.text.y = element_text(angle=180, 
                                          vjust=1,
                                          hjust=1),
              plot.margin = margin(t=0, b=0, unit="cm"),
              panel.grid.minor = element_blank(),
              panel.grid.major.x = element_blank(),
              panel.spacing.x = unit(0.3, "cm"),
              plot.background=element_rect(fill=plot_bg_color, color=plot_bg_color),
              panel.spacing.y = unit(0.3, "cm"))+
        scale_y_continuous(labels=scales::label_percent(accuracy=1),
                           minor_breaks = NULL,
                           limits=c(0,NA),
                           position = "right",
                           sec.axis = dup_axis())+
        scale_x_reordered()+
        scale_color_manual(values=colors_ethnicity, na.value="grey")+
        #scale_color_paletteer_d("ggsci::default_jama")+
        facet_row(~ethnicity,
                  # switch = "y",
                  scales="free_x",
                  space="free"))
